Value-Suppressing Uncertainty Maps

### 2017-03-31 paper/template.tex
Show flow
check in

The general VSUM algorithm is as follows:

@@

For each task, participants saw one of three types of thematic maps. Either two \textbf{juxtaposed} maps side-by-side, with separate encodings for value and uncertainty, a traditional \textbf{bivariate} map, where value and uncertainty are orthogonally encoded, or a \textbf{VSUM}. Figure \ref{fig:conditions} shows examples of these factor levels. Other factors included the size of the map (either a 4x4 or 8x8 grid), and (for the prediction task), the question framing (attack or defense). These secondary factors were evenly blocked across stimuli. Fatigue effects were significant in piloting, and so we limited the number of replicates: participants saw 18 stimuli (6 for each map type) for the identification task, and 12 (4 for each map type) for the prediction task.

@@

@@

\subsubsection{Prediction Task}

@@

\subsubsection{Hypotheses}

@@

@@

>>>>

\flowFig

The general VSUM algorithm demonstrated in \figref{fig:flow} is as follows:

@@

For each task, participants saw one of three types of thematic maps. Either two \textbf{juxtaposed} maps side-by-side, with separate encodings for value and uncertainty, a traditional \textbf{bivariate} map, where value and uncertainty are orthogonally encoded, or a \textbf{VSUM}. Figure \ref{fig:conditions} shows examples of these factor levels. Other factors included the size of the map (either a 4x4 or 8x8 grid), and (for the prediction task), the question framing (attack or defense). All factors were presented within subjects. Secondary factors were evenly blocked across stimuli. Fatigue effects were significant in piloting, and so we limited the number of replicates: participants saw 18 stimuli (6 for each map type) for the identification task, and 12 (4 for each map type) for the prediction task.

@@

\subsection{Identification Task}

@@

\subsection{Prediction Task}

@@

\subsection{Hypotheses}

@@

Rather than standard means, Cleveland \& McGill~\cite{cleveland1984graphical} use 25\% trimmed means to report effect sizes in graphical perception tasks. Trimmed means remove the first and last quartiles and then compute the mean from the remaining points. This filtering is important for graphical perception tasks (especially crowdsourced tasks) where error distributions may be long-tailed~\cite{heer2010crowdsourcing}. Trimmed means violate the sampling assumptions required for many null-hypothesis significance tests. Thus, while we report effect sizes in terms of trimmed means, we perform statistical tests on the standard means.

@@

We performed a one-way ANOVA investigating the effect of chart type (juxtaposed, full bivariate, or VSUM) on accuracy. We found only a marginal effect $F(2,859) = 2.4$, $p=0.09$, although more trails with VSUMs were ($66\%$ of trials) compared to the other conditions ()

These results partially support our first hypothesis. While there
